MINOS Handover Plots

### 2024-10-15 minos/validation/handovers.Rmd
Adding Hughs poverty variable generation in generate_composite_vars, and the child material deprivation module and some additions to get that up and running. Also started the child material deprivation intervention class

density_plot_quintile(base.dat, int.dat, quintile = 1)
density_plot_quintile(base.dat, int.dat, quintile = 2)
density_plot_quintile(base.dat, int.dat, quintile = 3)
density_plot_quintile(base.dat, int.dat, quintile = 4)
density_plot_quintile(base.dat, int.dat, quintile = 5)
```

@@

mean_income_quintile(base.dat, int.dat)
```

@@

base <- base.dat %>%
  group_by(time, income_quint) %>%
  summarise(min = min(hh_income),
            max = max(hh_income)) %>%
  mutate(source = 'Baseline')
int <- int.dat %>%
  group_by(time, income_quint) %>%
  summarise(min = min(hh_income),
            max = max(hh_income)) %>%
  mutate(source = 'Intervention')

combined <- rbind(base, int)
combined$income_quint <- factor(combined$income_quint)

quintile_threshold_plot <- function(data, year) {
  ggplot(filter(data, time == year), 
         aes(x = income_quint, y = min,
             ymin = min, lower = min, ymax = max, upper = max,
             group = source, 
             colour = source, 
             fill = source)) +
    geom_crossbar(position = position_dodge()) +
    labs(title = 'Quintile Thresholds',
         subtitle = year)
}

quintile_threshold_plot(combined, year = 2020)
quintile_threshold_plot(combined, year = 2021)
quintile_threshold_plot(combined, year = 2025)
quintile_threshold_plot(combined, year = 2030)
quintile_threshold_plot(combined, year = 2035)
```

@@

```{r}
raw.sf12 <- raw.dat %>%
  select(pidp, age, time, SF_12, SF_12_diff)
base.sf12 <- base.dat %>%
  select(pidp, age, time, SF_12, SF_12_diff)

sf12.spag <- rbind(raw.sf12, base.sf12)

sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
spaghetti_plot(sf12.spag.sample, 'SF_12',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
               save = shall.we.save,
               save.path = save.path)

spaghetti_plot(sf12.spag.sample, 'SF_12_diff',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12_diff',
               save = shall.we.save,
               save.path = save.path)

density_ridges(sf12.spag, "SF_12", 
               save = T, 
               save.path = save.path)

rm(raw.sf12, base.sf12, sf12.spag)
```

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, nkids)
base.s <- base.dat %>%
  select(pidp, age, time, nkids)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'nkids',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

```{r}
raw.s <- raw.parity %>%
  select(pidp, age, time, nkids_ind)
base.s <- base.parity %>%
  select(pidp, age, time, nkids_ind)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'nkids_ind',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

```{r}
handover_boxplots(raw.dat, base.dat, 'hourly_wage')
handover_lineplots(raw.dat, base.dat, 'hourly_wage')
```

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, hourly_wage)
base.s <- base.dat %>%
  select(pidp, age, time, hourly_wage)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'hourly_wage',
               save = shall.we.save,
               save.path = save.path)

# now a version limited to 0-100
spag <- spag %>%
  filter(hourly_wage <= 300)
spaghetti_plot(spag, 'hourly_wage',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

>>>>

# density_plot_quintile(base.dat, int.dat, quintile = 1)
# density_plot_quintile(base.dat, int.dat, quintile = 2)
# density_plot_quintile(base.dat, int.dat, quintile = 3)
# density_plot_quintile(base.dat, int.dat, quintile = 4)
# density_plot_quintile(base.dat, int.dat, quintile = 5)
```

@@

#mean_income_quintile(base.dat, int.dat)
```

@@

# base <- base.dat %>%
#   group_by(time, income_quint) %>%
#   summarise(min = min(hh_income),
#             max = max(hh_income)) %>%
#   mutate(source = 'Baseline')
# int <- int.dat %>%
#   group_by(time, income_quint) %>%
#   summarise(min = min(hh_income),
#             max = max(hh_income)) %>%
#   mutate(source = 'Intervention')
# 
# combined <- rbind(base, int)
# combined$income_quint <- factor(combined$income_quint)
# 
# quintile_threshold_plot <- function(data, year) {
#   ggplot(filter(data, time == year), 
#          aes(x = income_quint, y = min,
#              ymin = min, lower = min, ymax = max, upper = max,
#              group = source, 
#              colour = source, 
#              fill = source)) +
#     geom_crossbar(position = position_dodge()) +
#     labs(title = 'Quintile Thresholds',
#          subtitle = year)
# }
# 
# quintile_threshold_plot(combined, year = 2020)
# quintile_threshold_plot(combined, year = 2021)
# quintile_threshold_plot(combined, year = 2025)
# quintile_threshold_plot(combined, year = 2030)
# quintile_threshold_plot(combined, year = 2035)
```

@@

```{r}
# raw.sf12 <- raw.dat %>%
#   select(pidp, age, time, SF_12, SF_12_diff)
# base.sf12 <- base.dat %>%
#   select(pidp, age, time, SF_12, SF_12_diff)
# 
# sf12.spag <- rbind(raw.sf12, base.sf12)
# 
# sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
# spaghetti_plot(sf12.spag.sample, 'SF_12',
#                save = shall.we.save,
#                save.path = save.path)
# spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
#                save = shall.we.save,
#                save.path = save.path)
# 
# spaghetti_plot(sf12.spag.sample, 'SF_12_diff',
#                save = shall.we.save,
#                save.path = save.path)
# spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12_diff',
#                save = shall.we.save,
#                save.path = save.path)
#   
# density_ridges(sf12.spag, "SF_12", 
#                save = T, 
#                save.path = save.path)
# 
# rm(raw.sf12, base.sf12, sf12.spag)
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, nkids)
# base.s <- base.dat %>%
#   select(pidp, age, time, nkids)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'nkids',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

```{r}
# raw.s <- raw.parity %>%
#   select(pidp, age, time, nkids_ind)
# base.s <- base.parity %>%
#   select(pidp, age, time, nkids_ind)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'nkids_ind',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

## CHILD POVERTY VARS

### Relative poverty

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'relative_poverty')

tit <- 'Relative Poverty'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = relative_poverty, colour = relative_poverty)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=relative_poverty)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'relative_poverty.png',
         plot = last_plot(),
         path = save.path)
}

### Absolute Poverty

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'absolute_poverty')

tit <- 'Absolute Poverty'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = absolute_poverty, colour = absolute_poverty)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=absolute_poverty)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'absolute_poverty.png',
         plot = last_plot(),
         path = save.path)
}

### Persistent Poverty

```{r}
# prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'persistent_poverty')
# 
# var <- prepped.list$var
# norm <- prepped.list$norm
# 
# tit <- 'Persistent Poverty'
# 
# # Now plot
# ggplot(data = var, mapping = aes(x = time, y = n, group = persistent_poverty, colour = persistent_poverty)) +
#   geom_line() +
#   geom_vline(xintercept=start.year, linetype='dotted') +
#   labs(title = tit, subtitle = 'Counts by Level') +
#   xlab('Year') +
#   ylab('Count')
# 
# ggplot(data = norm, mapping = aes(x = time, y = prct, fill=persistent_poverty)) +
#   geom_bar(stat = 'identity') +
#   geom_vline(xintercept=start.year, linetype='dotted') +
#   labs(title = tit) +
#   xlab('Year') +
#   ylab('Proportion')
# 
# if (shall.we.save) {
#   ggsave(filename = 'persistent_poverty.png',
#          plot = last_plot(),
#          path = save.path)
# }
# 
# 
# rm(prepped.list, var, norm, tit)

### Low Income and Material Deprivation

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'low_income_matdep_child')

tit <- 'Material Deprivation Child'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = low_income_matdep_child, colour = low_income_matdep_child)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=low_income_matdep_child)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'low_income_matdep_child.png',
         plot = last_plot(),
         path = save.path)
}

rm(prepped.list, var, norm, tit)

@@

```{r}
# handover_boxplots(raw.dat, base.dat, 'hourly_wage')
# handover_lineplots(raw.dat, base.dat, 'hourly_wage')
```

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, hourly_wage)
# base.s <- base.dat %>%
#   select(pidp, age, time, hourly_wage)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'hourly_wage',
#                save = shall.we.save,
#                save.path = save.path)
# 
# # now a version limited to 0-100
# spag <- spag %>%
#   filter(hourly_wage <= 300)
# spaghetti_plot(spag, 'hourly_wage',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```
